Software Ticket Quality

### 2017-11-15 proposal/mprop.tex
Fix bug in rendering tex file
Finish paper on data quality assessment

% TODO: complete this paper
\textbf{Product perspective on total 
        Data Quality Assessment}\cite{wang1998product}:
\begin{itemize}
  \item \textbf{What were the goals?}

  \item \textbf{What was the method?}
    They created the TDQM methodology which is based on accumulated research 
    and extended 
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

@@

\textbf{Do Stack Traces Help Developers Fix Bugs?}\cite{schroter2010stack}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to identify if including a stack trace in a 
    bug report would help the developers fix the issue quicker. They divided their
    investigations in order to follow 4 research questions:
      \begin{itemize}
        \item are bugs fixed in methods in stack traces;
        \item how far down the stack to trace;
        \item are two or more stack traces better than one;
        \item do stack traces help speed up debugging.
  \item \textbf{What was the method?}
    They conducted their investigation on the Eclipse project which is developed in
    Java. Then, they extracted stack traces from bug reports using the infoZilla tool.
    Afterwards, they linked the stack traces (and thus the corresponding bug report)
    to changes in the source code (change logs) by mining the version repository of the
    Eclipse project.
  \item \textbf{What did they learn?}
    They found answers to all their research questions, and are as follows:
      \begin{itemize}
        \item around 60\% of the bugs that contained stack traces were fixed in 
        one of the methods in the frames;
        \item around 40\% were fixed in the first stack frame, around 80\% were fixed
        within the top 6 frames, while close to 90\% of the bugs were fixed within top 10 stack frames;
        \item having more than one stack trace usually helped more than only a single one;
        \item bug reports containing stack traces usually have a shorter lifetime, thus
        speeding up the debugging process.
      \end{itemize}
  \item \textbf{Relevance to our work}:
    Stack traces are one of the types of information we are investigating in our research
    and it is very useful to have such a study back up the statement that stack traces are
    valuable for developers so that they speed up the issue fixing process.
\end{itemize}

>>>>

\textbf{Product perspective on total Data Quality Assessment}\cite{wang1998product}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The author wanted to create a Total Data Quality Management methodology so that
    high quality information products could be delivered to information consumers.
  \item \textbf{What was the method?}
    The research presents us, firstly, with a couple of definitions for the methodology:
      \begin{itemize}
        \item TDQM cycle - define, measure, analyze and improve information quality continuously;
        \item information product - information output from an information manufacturing system
          that has value to the information consumer;
        \item information quality - fitness for use by information consumers.
      \end{itemize}
    Then, the author presents the four steps in order to successfully implement the TDQM methodology:
      \begin{itemize}
        \item clearly articulate the information product;
        \item establish several roles that would be in charge of the information product management;
        \item teach information quality assessment and management skills to all IP constituencies;
        \item institutionalize continuous information product improvement.
      \end{itemize}
  \item \textbf{What did they learn?}
    The author learned that this methodology is filling a gap in the information quality
    world and that it could help organizations better manage the information quality of their
    information products.
  \item \textbf{Relevance to our work}
    This article could prove helpful to our own research as the methodology presented could help
    us in detecting if there is data quality in the projects we will be analyzing.
\end{itemize}

@@

\textbf{Do Stack Traces Help Developers Fix Bugs?}\cite{schroter2010stack}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to identify if including a stack trace in a 
    bug report would help the developers fix the issue quicker. They divided their
    investigations in order to follow 4 research questions:
      \begin{itemize}
        \item are bugs fixed in methods in stack traces;
        \item how far down the stack to trace;
        \item are two or more stack traces better than one;
        \item do stack traces help speed up debugging.
      \end{itemize}
  \item \textbf{What was the method?}
    They conducted their investigation on the Eclipse project which is developed in
    Java. Then, they extracted stack traces from bug reports using the infoZilla tool.
    Afterwards, they linked the stack traces (and thus the corresponding bug report)
    to changes in the source code (change logs) by mining the version repository of the
    Eclipse project.
  \item \textbf{What did they learn?}
    They found answers to all their research questions, and are as follows:
      \begin{itemize}
        \item around 60\% of the bugs that contained stack traces were fixed in 
        one of the methods in the frames;
        \item around 40\% were fixed in the first stack frame, around 80\% were fixed
        within the top 6 frames, while close to 90\% of the bugs were fixed within top 10 stack frames;
        \item having more than one stack trace usually helped more than only a single one;
        \item bug reports containing stack traces usually have a shorter lifetime, thus
        speeding up the debugging process.
      \end{itemize}
  \item \textbf{Relevance to our work}:
    Stack traces are one of the types of information we are investigating in our research
    and it is very useful to have such a study back up the statement that stack traces are
    valuable for developers so that they speed up the issue fixing process.
\end{itemize}
